---
output: html_document
---

```{r, include=FALSE}
source("../../../../../../R/Functions.R", local = knitr::knit_global())
```

You can search for ready4 modules and sub-modules using tools from the ready4 R package. 
<br/><br/>

```{r message=FALSE, warning=FALSE}
library(ready4)
```

<br/><br/>
A table of ready4 modules and sub-modules can be generated by scraping ready4 R package websites using the `make_modules_tb` function (this may take a couple of minutes).
<br/><br/>

```{r}
modules_tb <-  make_modules_tb()
```

<br/><br/>
A slightly quicker method to achieve a similar (but potentially less up to date) result is to use the `get_modules_tb` function.
<br/><br/>

```{r eval=FALSE}
# Not run
# modules_tb <- get_modules_tb()
```

<br/><br/>
If you wish to display the table of modules as HTML, you can use the `print_modules` function. You can choose to display only ready4 modules (which always use R's "S4" class type).
<br/><br/>

```{r eval=FALSE}
print_modules(modules_tb,
              what_1L_chr = "S4")
```
<br/><br/>

```{r echo=FALSE}
print_modules(modules_tb,
              what_1L_chr = "S4")
```

<br/><br/>
You can also choose to display only ready4 sub-modules (which always use R's "S3" class type).
<br/><br/>

```{r eval=FALSE}
print_modules(modules_tb,
              what_1L_chr = "S3")
```
<br/><br/>

```{r echo=FALSE}
print_modules(modules_tb,
              what_1L_chr = "S3")
```